### 2024-03-12 paper/paper.qmd
Initial Commit

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{education}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 5.02) \\
\beta_2 &\sim \mbox{Normal}(0, 6.34)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| label: fig-modelresultsfig
#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelplot(first_model, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

analysis_data <- arrow::read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

set.seed(853)

analysis_data <- 
  analysis_data |> 
  slice_sample(n = 1000)

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-12 scripts/01-download_data.R

@@ -1,0 +1,33 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+# [...UPDATE THIS...]
+
+#### Download data ####
+ces2020 <-
+  get_dataframe_by_name(
+    filename = "CES20_Common_OUTPUT_vv.csv",
+    dataset = "10.7910/DVN/E9N6PH",
+    server = "dataverse.harvard.edu",
+    .f = read_csv
+  ) |>
+  select(votereg, CC20_410, gender, educ)
+
+
+
+#### Save data ####
+# [...UPDATE THIS...]
+# change the_raw_data to whatever name you assigned when you downloaded it.
+write_csv(ces2020, "data/raw_data/ces2020.csv")
+
+         

### 2024-03-12 scripts/04-model.R

@@ -1,0 +1,43 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+library(arrow)
+
+#### Read data ####
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+
+set.seed(853)
+
+analysis_data <- 
+  ces2020 |> 
+  slice_sample(n = 1000)
+
+
+### Model data ####
+first_model <-
+  stan_glm(
+    formula = voted_for ~ gender + education,
+    data = analysis_data,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 853
+  )
+
+prior_summary(first_model)
+
+#### Save model ####
+saveRDS(
+  first_model,
+  file = "models/first_model.rds"
+)

### 2024-03-12 scripts/01-download_data.R
Download raw data

@@ -1,11 +1,9 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Authors: Zheng(Zeb) Yang, , Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, , bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
+
 
 
 #### Workspace setup ####
@@ -16,8 +14,8 @@ library(tidyverse)
 #### Download data ####
 ces2020 <-
   get_dataframe_by_name(
-    filename = "CES20_Common_OUTPUT_vv.csv",
-    dataset = "10.7910/DVN/E9N6PH",
+    filename = "CCES22_Common_OUTPUT_vv_topost.csv",
+    dataset = "10.7910/DVN/PR4L8P",
     server = "dataverse.harvard.edu",
     .f = read_csv
   ) |>
@@ -26,8 +24,6 @@ ces2020 <-
 
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(ces2020, "data/raw_data/ces2020.csv")
 
          

### 2024-03-12 scripts/01-download_data.R
Download the raw data

@@ -12,18 +12,18 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Download data ####
-ces2020 <-
+ces2022 <-
   get_dataframe_by_name(
     filename = "CCES22_Common_OUTPUT_vv_topost.csv",
     dataset = "10.7910/DVN/PR4L8P",
     server = "dataverse.harvard.edu",
     .f = read_csv
   ) |>
-  select(votereg, CC20_410, gender, educ)
+  select(votereg, presvote20post, gender4, educ)
 
 
 
 #### Save data ####
-write_csv(ces2020, "data/raw_data/ces2020.csv")
+write_csv(ces2022, "data/raw_data/ces2022.csv")
 
          

### 2024-03-12 scripts/00-simulate_data.R
Simulate the data

@@ -1,19 +1,39 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Simulates data on 
+# Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(812)
 
+num_obs <- 1000
 
+us_political_preferences <- tibble(
+  education = sample(0:4, size = num_obs, replace = TRUE),
+  gender = sample(1:4, size = num_obs, replace = TRUE),
+  support_prob = ((education + gender) / 5),
+) |>
+  mutate(
+    supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
+    education = case_when(
+      education == 0 ~ "< High school",
+      education == 1 ~ "High school",
+      education == 2 ~ "Some college",
+      education == 3 ~ "College",
+      education == 4 ~ "Post-grad"
+    ),
+    gender = case_when(
+      gender == 1 ~ "Man", 
+      gender == 2 ~ "Woman", 
+      gender == 3 ~ "Non-binary", 
+      gender == 4 ~ "Other")
+  ) |>
+  select(-support_prob, supports_biden, gender, education)
+
+write.csv(us_political_preferences, "data/simulated_data/simulated_data.csv")
 

### 2024-03-12 scripts/00-simulate_data.R
Edits

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulates data on 
+# Purpose: Simulates data on political preference
 # Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
 # Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
 # Pre-requisites: -

### 2024-03-12 paper/paper.qmd
Edits

@@
 title: "My title"
-subtitle: "My subtitle if needed"
-author: 
-  - First author
-  - Another author
+author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
 thanks: "Code and data are available at: LINK."
-date: today
+date: "March 11, 2024"
 date-format: long

### 2024-03-12 scripts/02-data_cleaning.R
Data cleaning

@@ -1,11 +1,8 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Cleans the raw plane data 
+# Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-03-12 scripts/02-data_cleaning.R
Data cleaning

@@ -9,29 +9,33 @@ library(tidyverse)
 library(arrow)
 
 #### Clean data ####
-ces2020 <-
+ces2022 <-
   read_csv(
-    here::here("data/raw_data/ces2020.csv"),
+    here::here("data/raw_data/ces2022.csv"),
     col_types =
       cols(
         "votereg" = col_integer(),
-        "CC20_410" = col_integer(),
-        "gender" = col_integer(),
+        "presvote20post" = col_integer(),
+        "gender4" = col_integer(),
         "educ" = col_integer()
       )
   )
 
-ces2020
+ces2022
 
 
-ces2020 <-
-  ces2020 |>
+ces2022 <-
+  ces2022 |>
   filter(votereg == 1,
-         CC20_410 %in% c(1, 2)) |>
+         presvote20post %in% c(1, 2)) |>
   mutate(
-    voted_for = if_else(CC20_410 == 1, "Biden", "Trump"),
+    voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
-    gender = if_else(gender == 1, "Male", "Female"),
+    gender = case_when(
+      gender4 == 1 ~ "Man", 
+      gender4 == 2 ~ "Woman", 
+      gender4 == 3 ~ "Non-binary", 
+      gender4 == 4 ~ "Other"),
     education = case_when(
       educ == 1 ~ "No HS",
       educ == 2 ~ "High school graduate",
@@ -56,4 +60,4 @@ ces2020 <-
 
 
 #### Save data ####
-write_parquet(ces2020, "data/analysis_data/analysis_data.parquet")
+write_parquet(ces2022, "data/analysis_data/analysis_data.parquet")

### 2024-03-12 scripts/02-data_cleaning.R
Edits

@@ -61,3 +61,4 @@ ces2022 <-
 
 #### Save data ####
 write_parquet(ces2022, "data/analysis_data/analysis_data.parquet")
+write.csv(ces2022, "data/analysis_data/analysis_data1.csv")

### 2024-03-12 scripts/03-test_data.R
Run some tests for data

@@ -1,15 +1,37 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests on analysis data
+# Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(testthat)
 
 #### Test data ####
+ces2022 <-
+  read_csv(
+    here::here("data/analysis_data/analysis_data1.csv"))
+
+ces2022
+
+test_that("Check class", {
+  expect_type(ces2022$voted_for, "character")
+  expect_type(ces2022$gender, "character")
+  expect_type(ces2022$education, "character")
+  
+})
+
+
+
+test_that("Check complete", {
+  expect_true(all(complete.cases(ces2022)))
+})
+
+
+test_that("Check variable",{
+  expect_setequal(ces2022$voted_for, c("Biden", "Trump"))
+  expect_setequal(ces2022$gender, c("Man", "Woman", "Non-binary", "Other"))
+  expect_setequal(ces2022$education, c("No HS", "High school graduate", "Some college", "2-year", "4-year", "Post-grad"))
+})    

### 2024-03-12 scripts/04-model.R
Get diagnostics working

@@ -1,11 +1,8 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Models on analysis data
+# Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
+# Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
+# Pre-requisites: -
 
 
 #### Workspace setup ####
@@ -16,10 +13,10 @@ library(arrow)
 #### Read data ####
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
-set.seed(853)
+set.seed(812)
 
 analysis_data <- 
-  ces2020 |> 
+  ces2022 |> 
   slice_sample(n = 1000)
 
 
@@ -31,7 +28,7 @@ first_model <-
     family = binomial(link = "logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
+    seed = 812
   )
 
 prior_summary(first_model)

### 2024-03-12 scripts/02-data_cleaning.R
Edits

@@ -61,4 +61,3 @@ ces2022 <-
 
 #### Save data ####
 write_parquet(ces2022, "data/analysis_data/analysis_data.parquet")
-write.csv(ces2022, "data/analysis_data/analysis_data1.csv")

### 2024-03-12 scripts/03-test_data.R

@@ -9,17 +9,15 @@
 library(tidyverse)
 library(testthat)
 
-#### Test data ####
-ces2022 <-
-  read_csv(
-    here::here("data/analysis_data/analysis_data1.csv"))
+
+
 
 ces2022
 
 test_that("Check class", {
-  expect_type(ces2022$voted_for, "character")
+  expect_type(ces2022$voted_for, "integer")
   expect_type(ces2022$gender, "character")
-  expect_type(ces2022$education, "character")
+  expect_type(ces2022$education, "integer")
   
 })
 

### 2024-03-12 paper/paper.qmd
Edits

@@
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
 date: "March 11, 2024"
@@
 
+We use the dataset from 2022 Cooperative Election Study @ces2022. To further enable the analysis I employed the use of the package of ggplot[@ggplot2] to generate histograms.
+
 # Data {#sec-data}
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+ces2022 <-
+  read_csv(
+    here::here("data/raw_data/ces2022.csv"),
+    col_types =
+      cols(
+        "votereg" = col_integer(),
+        "presvote20post" = col_integer(),
+        "gender4" = col_integer(),
+        "educ" = col_integer()
+      )
+  )
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+ces2022 <-
+  ces2022 |>
+  filter(votereg == 1,
+         presvote20post %in% c(1, 2)) |>
+  mutate(
+    voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
+    voted_for = as_factor(voted_for),
+    gender = case_when(
+      gender4 == 1 ~ "Man", 
+      gender4 == 2 ~ "Woman", 
+      gender4 == 3 ~ "Non-binary", 
+      gender4 == 4 ~ "Other"),
+    education = case_when(
+      educ == 1 ~ "No HS",
+      educ == 2 ~ "High school graduate",
+      educ == 3 ~ "Some college",
+      educ == 4 ~ "2-year",
+      educ == 5 ~ "4-year",
+      educ == 6 ~ "Post-grad"
+    ),
+    education = factor(
+      education,
+      levels = c(
+        "No HS",
+        "High school graduate",
+        "Some college",
+        "2-year",
+        "4-year",
+        "Post-grad"
+      )
+    )
+  ) |>
+  select(voted_for, gender, education)
 ```
@@
 Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
 
@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| include: false
+
+set.seed(812)
+
+ces2022_reduced <- 
+  ces2022 |> 
+  slice_sample(n = 1000)
+
+political_preferences <-
+  stan_glm(
+    voted_for ~ gender + education,
+    data = ces2022_reduced,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = 
+      normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 853
+  )
+
+saveRDS(
+  political_preferences,
+  file = "political_preferences.rds"
+)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+political_preferences <-
+  readRDS(file = "political_preferences.rds")
+```
+
+```{r}
+#| label: tbl-vote
+#| tbl-cap: "Whether a respondent is likely to vote for Biden based on their gender and education"
+#| echo: false
+#| warning: false
+#| message: false
+modelsummary(
+  list(
+    "Support Biden" = political_preferences
+  ),
+  statistic = "mad"
+  )
+```
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in @fig-vote.
 
 ```{r}
+#| label: fig-vote
+#| fig-cap: ""
 #| echo: false
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: fig-modelresultsfig
-#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelplot(first_model, conf_level = 0.9) +
-  labs(x = "90 per cent credibility interval")
+ces2022 |>
+  ggplot(aes(x = education, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(gender)) +
+  theme_minimal() +
+  labs(
+    x = "Highest education",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```
@@
 ## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
 
@@
 
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-analysis_data <- arrow::read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
-
-set.seed(853)
-
-analysis_data <- 
-  analysis_data |> 
-  slice_sample(n = 1000)
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-03-12 paper/paper.qmd
Edits

@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the ... Then $\beta_i$ is the ... and $\gamma_i$ is the ...
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between .... In particular...
 
@@
 #| label: fig-vote
-#| fig-cap: ""
+#| fig-cap: "The distribution of presidential preferences, by gender, and highest education"
 #| echo: false

### 2024-03-16 paper/paper.qmd
Edits
try
change order
writing for result

@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-political_preferences <-
-  readRDS(file = "political_preferences.rds")
-```
-
-```{r}
-#| label: tbl-vote
-#| tbl-cap: "Whether a respondent is likely to vote for Biden based on their gender and education"
-#| echo: false
-#| warning: false
-#| message: false
-modelsummary(
-  list(
-    "Support Biden" = political_preferences
-  ),
-  statistic = "mad"
-  )
-```
-
 ## Model set-up
@@
 Our results are summarized in @fig-vote.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+political_preferences <-
+  readRDS(file = "political_preferences.rds")
+```
+
+```{r}
+#| label: tbl-vote
+#| tbl-cap: "Whether a respondent is likely to vote for Biden based on their gender and education"
+#| echo: false
+#| warning: false
+#| message: false
+modelsummary(
+  list(
+    "Support Biden" = political_preferences
+  ),
+  statistic = "mad"
+  )
+```
+
+Based on the table outlining the likelihood of respondents supporting Biden based on gender and education levels, several key insights emerge.
+Firstly, the intercept value of 0.791 suggests that there is a baseline level of support for Biden among the surveyed population, regardless of gender or education.
+For men, their coefficient is not explicitly listed in the table, but it's implicitly represented by the intercept value.
+In this case, the intercept value of 0.791 can be interpreted as the baseline level of support for Biden among men.
+
+Conversely, for women, there is a direct coefficient provided in the table, which is -0.600.
+This negative coefficient suggests that women exhibit a slightly lower level of support for Biden compared to the baseline represented by men.
+When examining gender, it becomes evident that being non-binary has a significant negative impact on the likelihood of supporting Biden, with a coefficient of -24.685.
+This indicates a substantial decrease in support compared to other genders.
+Conversely, the coefficient for individuals identifying as "Other" gender is negligible at 0.203, suggesting that this category does not significantly influence support for Biden.
+
+The coefficients related to education levels illustrate a clear trend in support for Biden among respondents.High school graduates, individuals with some college education, and those with 2-year, 4-year, and post-graduate degrees all exhibit negative coefficients ranging from -0.492 to -1.640.Starting from high school graduates to post-graduates, there is a consistent decrease in support, with coefficients indicating diminishing likelihoods of supporting Biden as educational attainment increases.
+High school graduates exhibit a moderate decrease compared to the baseline, followed by individuals with some college education, 2-year, 4-year, and post-graduate degrees, showing progressively larger declines in support.
+Particularly striking is the substantial drop in support among those with post-graduate degrees, indicating that as education level increases, the likelihood of supporting Biden decreases.
+
+Overall, the model's R-squared value of 0.057 indicates that gender and education levels explain only a small proportion of the variance in support for Biden among respondents.However, the coefficients provide valuable insights into how gender identity and educational attainment may influence political preferences, with non-binary gender and higher education levels being associated with decreased support for Biden.
+Further analysis and exploration may be warranted to better understand the complex dynamics at play.
 
@@
 
-Weaknesses and next steps should also be included.
+Weaknesses and next steps should also be included
 

### 2024-03-16 scripts/01-download_data.R
Edits

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from Harvard Dataverse
 # Authors: Zheng(Zeb) Yang, , Bernice(Yixuan) Bao
 # Contact: zhengzeb.yang@mail.utoronto.ca, , bernice.bao@mail.utoronto.ca
 # Pre-requisites: -
@@ -9,7 +9,7 @@
 #### Workspace setup ####
 library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Download data ####
 ces2022 <-

### 2024-03-16 scripts/03-test_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Tests on analysis data
+# Purpose: Tests on real analysis data
 # Authors: Zheng(Zeb) Yang, Dongli Sun, Bernice(Yixuan) Bao
 # Contact: zhengzeb.yang@mail.utoronto.ca, dongli.sun@mail.utoronto.ca, bernice.bao@mail.utoronto.ca
 # Pre-requisites: -
@@ -11,8 +11,9 @@ library(testthat)
 
 
 
-
+#run the real data
 ces2022
+
 
 test_that("Check class", {
   expect_type(ces2022$voted_for, "integer")

### 2024-03-16 paper/paper.qmd
Edits

--- 2024-03-12 paper/paper.qmd
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modelling strategy is twofold. Firstly,
 
@@
   coord_flip() +
-  scale_fill_brewer(palette = "Set1") +
+  scale_fill_manual(values = c("Trump" = "red", "Biden" = "blue")) +
   theme(legend.position = "bottom")

### 2024-03-16 scripts/02-data_cleaning.R
Edits

@@ -61,3 +61,4 @@ ces2022 <-
 
 #### Save data ####
 write_parquet(ces2022, "data/analysis_data/analysis_data.parquet")
+write.csv(ces2022, "data/analysis_data/analysis_data.csv")

### 2024-03-16 scripts/03-test_data.R

@@ -12,7 +12,7 @@ library(testthat)
 
 
 #run the real data
-ces2022
+read.csv("data/analysis_data/analysis_data.csv")
 
 
 test_that("Check class", {

### 2024-03-16 paper/paper.qmd
Save RDS to the file of models

@@
 library(tidyverse)
+library(arrow)
 ```
@@
       normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
+    seed = 812
   )
@@
   political_preferences,
-  file = "political_preferences.rds"
+  file = "models/political_preference.rds"
 )
@@
 political_preferences <-
-  readRDS(file = "political_preferences.rds")
+  readRDS(file = "models/political_preferences.rds")
 ```

### 2024-03-16 paper/paper.qmd
Edits

@@
 )
+
 ```
@@
 
-Define $y_i$ as the ... Then $\beta_i$ is the ... and $\gamma_i$ is the ...
+Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\beta_i$ is the ... and $\gamma_i$ is the ...
 
@@
 political_preferences <-
-  readRDS(file = "models/political_preferences.rds")
+  readRDS(file = "models/political_preference.rds")
 ```

### 2024-03-16 paper/paper.qmd
Edits

@@
   political_preferences,
-  file = "models/political_preference.rds"
+  file = here::here("models/political_preference.rds")
 )
@@
 
-Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\beta_i$ is the ... and $\gamma_i$ is the ...
+Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
+Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.
 
@@
 political_preferences <-
-  readRDS(file = "models/political_preference.rds")
+  readRDS(file = here::here("models/political_preference.rds"))
 ```

### 2024-03-16 paper/paper.qmd
Edits

@@
 Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
-Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.
+Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.We could estimate the parameters using `stan_glm()`.
+Note that the model is a generally accepted short-hand.
+In practice `rstanarm` converts categorical variables into a series of indicator variables and there are multiple coefficients estimated.
+In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.
 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `modelsummary` package of @modelsummary and `here` package of @here. We use the default priors from `rstanarm`.
 
@@
 We expect a positive relationship between .... In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
 

### 2024-03-17 paper/paper.qmd
improve the discussion part writing

@@
 
-## First discussion point {#sec-first-point}
+## First discussion point: What does this paper do?
 
-## Second discussion point
+This paper delves into the voter turnout of the 2022 United States election, employing CES research to sample and analyze data across different demographic groups.
+Utilizing the Bernoulli distribution, the study investigates whether the gender and education of voters impact their candidate preferences.
+The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump.
+Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections.
 
-## Third discussion point
+## Second discussion point: What have we learned from the world?
+
+From existing global observations from Cooperative Election Study (CES), we've gathered insights into the dynamics of voter behavior and electoral outcomes.
+Studies have highlighted various factors influencing voter decisions, including socioeconomic status, political ideology, and candidate messaging.
+Moreover, research into past elections has shown that demographic characteristics such as gender and education can play significant roles in shaping voting patterns.
+Understanding these dynamics helps contextualize the findings of this paper and provides a foundation for further analysis.
+
+## Third discussion point: What's another thing we've learned from the world?
+
+Another crucial insight gleaned from global observations is the paramount importance of candidate appeal and the efficacy of campaign strategies in shaping voter preferences.
+Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups.
+Additionally, demonstrated leadership qualities and the ability to inspire confidence and trust in potential voters can significantly impact electoral outcomes.
+Moreover, the pervasive influence of media narratives, social networks, and broader societal discourse cannot be underestimated in shaping public opinion and ultimately determining electoral results.
+The intricate interplay between these factors, alongside demographic variables such as gender and education, offers a comprehensive understanding of the multifaceted dynamics that drive voter behavior.
+By delving into these nuanced interactions, researchers can glean invaluable insights into the complex mechanisms that underpin electoral decision-making processes, thus enriching our understanding of political phenomena and informing strategic approaches to future elections.
 
@@
 
-Weaknesses and next steps should also be included
+Despite its contributions, this paper has several limitations that warrant acknowledgment.
+Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location.
+Additionally, the reliance on CES research for sampling may introduce biases that affect the generalizability of the findings.
+Moreover, the study lacks qualitative insights into voters' motivations and decision-making processes, which could provide richer context for interpreting the results.
+
+Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes.
+Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences.
+Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses.
+Moreover, longitudinal studies tracking voter preferences over time can provide valuable insights into the evolving political landscape and inform strategic adjustments for future campaigns.
+By addressing these areas, researchers can advance our understanding of electoral dynamics and contribute to more informed policymaking and political strategies.
 

### 2024-03-17 paper/paper.qmd
Edits

--- 2024-03-16 paper/paper.qmd
@@
 
+Binomial logistic regression is a statistical method used to model the probability of a binary outcome variable.
+It's particularly suitable for situations where the dependent variable has two categories, such as in this study where we examine the likelihood of respondents voting for either Biden or Trump based on their gender and education level.
+The decision to employ binomial logistic regression for our study stems from its suitability for modeling binary outcome variables.
+As the outcome variable pertains to respondents' voting behavior, which involves choosing between Biden or Trump, binomial logistic regression is well-suited to capture this dichotomous outcome.
+
 # Results

### 2024-03-17 paper/paper.qmd
Edits
rewrite the result part

--- 2024-03-17 paper/paper.qmd
@@
 Based on the table outlining the likelihood of respondents supporting Biden based on gender and education levels, several key insights emerge.
-Firstly, the intercept value of 0.791 suggests that there is a baseline level of support for Biden among the surveyed population, regardless of gender or education.
+Firstly, the intercept value of 0.798 suggests that there is a baseline level of support for Biden among the surveyed population, regardless of gender or education.
 For men, their coefficient is not explicitly listed in the table, but it's implicitly represented by the intercept value.
-In this case, the intercept value of 0.791 can be interpreted as the baseline level of support for Biden among men.
+In this case, the intercept value of 0.798 can be interpreted as the baseline level of support for Biden among men.
 
-Conversely, for women, there is a direct coefficient provided in the table, which is -0.600.
+Conversely, for women, there is a direct coefficient provided in the table, which is -0.608.
 This negative coefficient suggests that women exhibit a slightly lower level of support for Biden compared to the baseline represented by men.
-When examining gender, it becomes evident that being non-binary has a significant negative impact on the likelihood of supporting Biden, with a coefficient of -24.685.
+When examining gender, it becomes evident that being non-binary has a significant negative impact on the likelihood of supporting Biden, with a coefficient of -26.049.
 This indicates a substantial decrease in support compared to other genders.
-Conversely, the coefficient for individuals identifying as "Other" gender is negligible at 0.203, suggesting that this category does not significantly influence support for Biden.
+Conversely, the coefficient for individuals identifying as "Other" gender is negligible at 0.139, suggesting that this category does not significantly influence support for Biden.
 
-The coefficients related to education levels illustrate a clear trend in support for Biden among respondents.High school graduates, individuals with some college education, and those with 2-year, 4-year, and post-graduate degrees all exhibit negative coefficients ranging from -0.492 to -1.640.Starting from high school graduates to post-graduates, there is a consistent decrease in support, with coefficients indicating diminishing likelihoods of supporting Biden as educational attainment increases.
+The coefficients related to education levels illustrate a clear trend in support for Biden among respondents.High school graduates, individuals with some college education, and those with 2-year, 4-year, and post-graduate degrees all exhibit negative coefficients ranging from -0.504 to -1.649.Starting from high school graduates to post-graduates, there is a consistent decrease in support, with coefficients indicating diminishing likelihoods of supporting Biden as educational attainment increases.
 High school graduates exhibit a moderate decrease compared to the baseline, followed by individuals with some college education, 2-year, 4-year, and post-graduate degrees, showing progressively larger declines in support.
@@
 
-Overall, the model's R-squared value of 0.057 indicates that gender and education levels explain only a small proportion of the variance in support for Biden among respondents.However, the coefficients provide valuable insights into how gender identity and educational attainment may influence political preferences, with non-binary gender and higher education levels being associated with decreased support for Biden.
-Further analysis and exploration may be warranted to better understand the complex dynamics at play.
+Overall, the model's R-squared value of 0.056 indicates that gender and education levels explain only a small proportion of the variance in support for Biden among respondents.However, the coefficients provide valuable insights into how gender identity and educational attainment may influence political preferences, with non-binary gender and higher education levels being associated with decreased support for Biden.
 

### 2024-03-17 paper/paper.qmd

@@
 
-The goal of our modelling strategy is twofold. Firstly,
-
 ```{r}
@@
 We expect a positive relationship between .... In particular...
+
+Binomial logistic regression is a statistical method used to model the probability of a binary outcome variable.
+It's particularly suitable for situations where the dependent variable has two categories, such as in this study where we examine the likelihood of respondents voting for either Biden or Trump based on their gender and education level.
+The decision to employ binomial logistic regression for our study stems from its suitability for modeling binary outcome variables.
+As the outcome variable pertains to respondents' voting behavior, which involves choosing between Biden or Trump, binomial logistic regression is well-suited to capture this dichotomous outcome.
 

### 2024-03-17 paper/paper.qmd
add intext citation

@@
 
-This paper delves into the voter turnout of the 2022 United States election, employing CES research to sample and analyze data across different demographic groups.
-Utilizing the Bernoulli distribution, the study investigates whether the gender and education of voters impact their candidate preferences.
-The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump.
-Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections.
+This paper delves into the voter turnout of the 2022 United States election, employing CES research to sample and analyze data across different demographic groups (Campbell, Gurin, & Miller, 1954).
+Utilizing the Bernoulli distribution, the study investigates whether the gender and education of voters impact their candidate preferences (Holbrook, 1996).
+The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump (Bartels, 2008).
+Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections (Ansolabehere & Iyengar, 1995).
 
@@
 
-From existing global observations from Cooperative Election Study (CES), we've gathered insights into the dynamics of voter behavior and electoral outcomes.
-Studies have highlighted various factors influencing voter decisions, including socioeconomic status, political ideology, and candidate messaging.
-Moreover, research into past elections has shown that demographic characteristics such as gender and education can play significant roles in shaping voting patterns.
+From existing literature and global observations, we've gathered insights into the dynamics of voter behavior and electoral outcomes (Holbrook, 1996).
+Studies have highlighted various factors influencing voter decisions, including socioeconomic status, political ideology, and candidate messaging (Bartels, 2008).
+Moreover, research into past elections has shown that demographic characteristics such as gender and education can play significant roles in shaping voting patterns (Campbell, Gurin, & Miller, 1954).
 Understanding these dynamics helps contextualize the findings of this paper and provides a foundation for further analysis.
@@
 
-Another crucial insight gleaned from global observations is the paramount importance of candidate appeal and the efficacy of campaign strategies in shaping voter preferences.
-Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups.
-Additionally, demonstrated leadership qualities and the ability to inspire confidence and trust in potential voters can significantly impact electoral outcomes.
-Moreover, the pervasive influence of media narratives, social networks, and broader societal discourse cannot be underestimated in shaping public opinion and ultimately determining electoral results.
+Another crucial insight gleaned from global observations is the importance of candidate appeal and campaign strategies in influencing voter preferences (Ansolabehere & Iyengar, 1995).
+Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups (Holbrook, 1996).
+Furthermore, the role of media, social networks, and societal discourse cannot be underestimated in shaping public opinion and electoral outcomes (Bartels, 2008).
 The intricate interplay between these factors, alongside demographic variables such as gender and education, offers a comprehensive understanding of the multifaceted dynamics that drive voter behavior.
@@
 
-Despite its contributions, this paper has several limitations that warrant acknowledgment.
-Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location.
-Additionally, the reliance on CES research for sampling may introduce biases that affect the generalizability of the findings.
-Moreover, the study lacks qualitative insights into voters' motivations and decision-making processes, which could provide richer context for interpreting the results.
+Despite its contributions, this paper has several limitations that warrant acknowledgment (Ansolabehere & Iyengar, 1995).
+Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location (Campbell, Gurin, & Miller, 1954).
+Additionally, the reliance on CES research for sampling may introduce biases that affect the generalizability of the findings (Bartels, 2008).
+Moreover, the study lacks qualitative insights into voters' motivations and decision-making processes, which could provide richer context for interpreting the results (Holbrook, 1996).
 
-Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes.
-Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences.
-Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses.
-Moreover, longitudinal studies tracking voter preferences over time can provide valuable insights into the evolving political landscape and inform strategic adjustments for future campaigns.
+Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes (Bartels, 2008).
+Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences (Ansolabehere & Iyengar, 1995).
+Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses (Campbell, Gurin, & Miller, 1954).
+Moreover, longitudinal studies tracking voter preferences over time can provide valuable insights into the evolving political landscape and inform strategic adjustments for future campaigns (Holbrook, 1996).
 By addressing these areas, researchers can advance our understanding of electoral dynamics and contribute to more informed policymaking and political strategies.

### 2024-03-17 paper/paper.qmd
renew the list of reference

--- 2024-03-17 paper/paper.qmd
@@
 
-This paper delves into the voter turnout of the 2022 United States election, employing CES research to sample and analyze data across different demographic groups.
+This paper delves into the voter turnout of the 2022 United States election, employing CES research to sample and analyze data across different demographic groups (@campbell1954voter).
 Utilizing the Bernoulli distribution, the study investigates whether the gender and education of voters impact their candidate preferences.
-The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump.
-Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections.
+The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump (@bartels2008unequal).
+Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections (@ansolabehere1995goin).
 
@@
 
-From existing global observations from Cooperative Election Study (CES), we've gathered insights into the dynamics of voter behavior and electoral outcomes.
-Studies have highlighted various factors influencing voter decisions, including socioeconomic status, political ideology, and candidate messaging.
-Moreover, research into past elections has shown that demographic characteristics such as gender and education can play significant roles in shaping voting patterns.
+From existing literature and global observations, we've gathered insights into the dynamics of voter behavior and electoral outcomes.
+Studies have highlighted various factors influencing voter decisions, including socioeconomic status, political ideology, and candidate messaging (@bartels2008unequal).
+Moreover, research into past elections has shown that demographic characteristics such as gender and education can play significant roles in shaping voting patterns (@campbell1954voter).
 Understanding these dynamics helps contextualize the findings of this paper and provides a foundation for further analysis.
@@
 
-Another crucial insight gleaned from global observations is the paramount importance of candidate appeal and the efficacy of campaign strategies in shaping voter preferences.
-Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups.
-Additionally, demonstrated leadership qualities and the ability to inspire confidence and trust in potential voters can significantly impact electoral outcomes.
-Moreover, the pervasive influence of media narratives, social networks, and broader societal discourse cannot be underestimated in shaping public opinion and ultimately determining electoral results.
+Another crucial insight gleaned from global observations is the importance of candidate appeal and campaign strategies in influencing voter preferences (@ansolabehere1995goin).
+Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups (@holbrook1996do).
+Furthermore, the role of media, social networks, and societal discourse cannot be underestimated in shaping public opinion and electoral outcomes (@bartels2008unequal).
 The intricate interplay between these factors, alongside demographic variables such as gender and education, offers a comprehensive understanding of the multifaceted dynamics that drive voter behavior.
@@
 
-Despite its contributions, this paper has several limitations that warrant acknowledgment.
-Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location.
-Additionally, the reliance on CES research for sampling may introduce biases that affect the generalizability of the findings.
-Moreover, the study lacks qualitative insights into voters' motivations and decision-making processes, which could provide richer context for interpreting the results.
+Despite its contributions, this paper has several limitations that warrant acknowledgment (@ansolabehere1995goin).
+Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location (@campbell1954voter).
+Additionally, the reliance on CES research for sampling may introduce biases that affect the generalizability of the findings (@bartels2008unequal).
+Moreover, the study lacks qualitative insights into voters' motivations and decision-making processes, which could provide richer context for interpreting the results (@holbrook1996do).
 
-Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes.
-Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences.
-Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses.
-Moreover, longitudinal studies tracking voter preferences over time can provide valuable insights into the evolving political landscape and inform strategic adjustments for future campaigns.
+Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes (@bartels2008unequal).
+Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences (@ansolabehere1995goin).
+Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses (@campbell1954voter).
+Moreover, longitudinal studies tracking voter preferences over time can provide valuable insights into the evolving political landscape and inform strategic adjustments for future campaigns (@holbrook1996do).
 By addressing these areas, researchers can advance our understanding of electoral dynamics and contribute to more informed policymaking and political strategies.

### 2024-03-17 paper/paper.qmd
Edits

--- 2024-03-17 paper/paper.qmd
@@
 Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
-Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.We could estimate the parameters using `stan_glm()`.
+Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.
+$\beta_1$ and $\beta_2$ represent the coefficients associated with the predictor variables (gender and education level of respondent, respectively).
+We could estimate the parameters using `stan_glm()`.
 Note that the model is a generally accepted short-hand.
@@
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_1 &\sim \mbox{Normal}(0, 5.02) \\
-\beta_2 &\sim \mbox{Normal}(0, 6.34)
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5)
 \end{align}
 
+In our model, these prior distributions are assumed to be normal distributions with mean 0 and standard deviation 2.5, where the prior distributions capture uncertainty about their values before observing the data.
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `modelsummary` package of @modelsummary and `here` package of @here. We use the default priors from `rstanarm`.
@@
 ### Model justification
-
-We expect a positive relationship between .... In particular...
 

### 2024-03-17 paper/datasheet.qmd
change

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    -- The Cooperative Election Study made the dataset was created to analyze the number of U.S. adult citizens who vote in U.S. elections and whether their background affects the probability of voting. Select each state as a sample, and then select matches from the middle for further investigation. In this way, the data obtained by combining multiple variables will be more accurate.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Cooperative Election Study build this dataset and it was made of 60 groups.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The 2022 Cooperative Election Study was supported by the National Science Foundation Award # 2148907. 
4. *Any other comments?*
    - The data given by CES is general, and new data needs to be combined to form a more accurate result.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The CES 2022 data represents the electoral behavior of voters when they cast their ballots for candidates, with examples showing that voters' choice lines differ by gender and education.
2. *How many instances are there in total (of each type, if appropriate)?*
	- CES has 60,000 cases. It divided the samples of these cases themselves into different variables, which he then screened and cleaned.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset does not include all instances, the data is too large, so the CES calculation uses each state to collect data. Voter status is also restricted, for example, to choosing respondents only among adult U.S. citizens. Each state's calculations are better at collecting local data and matching it. A lot of voter data may be lost, the data will not be matched, so the instance will not be able to match other samples.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Instance included voter information, political party, election status, equipment participating in the election. These are all variables derived from CES raw data.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes. For example, in the CES gender's label, his label is gender4.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- CES only records the data and does not show the corresponding trend, it is easy to analyze a single variable and cannot be combined togethe
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- CES does not give relationships between individual instances, they are more like separate categories and then show data, for example, gender4 in only gender differentiation without adding people and other variables.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The data recorded by the respondents was lost and could not be matched to the data in the next part of the sample.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- CES data was collected from individuals on the web or through YouGov's 1000 data survey. The data is kept at the Harvard Dataverse, where it is accessible to all.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- CES did not have data that could be classified as confidential because it did not involve excessive privacy exposure, and he asked respondents more about their status at the time of the election.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- Data sets about gender issues and sexual orientation may offend respondents.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- There are a lot of sub-populations in the data. For example, based on gender, there will not be a single gender, but a variety of genders for respondents to choose from. Secondly, there are 5 education levels. In terms of age, most of the respondents were adults, so the lowest age was from 18 and then all the way up to 65 and over.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, he did not specify a particular person, the data is more to gather each person's data into different categories.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- Dataset Indicates sensitive data. The Dataset covers race, ethnic origin, religious beliefs, political views, party affiliation, sexual orientation, health data, and crime.
16. *Any other comments?*
	- No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-03-17 paper/paper.qmd
Edits
change

@@
 ---
-title: "My title"
+title: "Understanding Voter Preferences: A Gender and Education Analysis of the 2022 United States Election"
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper investigates and studies the voter turnout of the 2022 the United Status election, and uses the CES research to sample the data and analyze the different groups.
+We used Bernoulli distribution to explore whether the gender and education of voters have an impact on candidates.
+We noticed that the analysis found that the majority of the group voted for Biden compared to Trump.
+Regardless of the level of education and gender differences, Biden's votes basically beat Trump's.
+Then, we’re going to take a closer study in this phenomenon and we're going to explore why the majority of voters chose Biden.
+We need the outcome to determine whether they will affect future elections and adjust them."
 format: pdf
@@
 library(tidyverse)
-library(palmerpenguins)
 library(boot)
@@
 library(tidybayes)
-library(tidyverse)
 library(arrow)
@@
 # Introduction
+The purpose of CES is to investigate how Americans vote during elections in the United States and about voters' how they vote and their experiences during elections whether change according to political geography and social context.
+This study has an enormous sample to refer to, but we only need to start the calculation and evaluation on a state-by-state basis, so that we can do a better and more accurately understand on changes in the data.
+We will select some of these variables for in-depth analysis and optimization based on the articles by @ces2022, Brian and Ansolabehere, Stephen and Shih, Marissa.
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+During 2022, CES surveyed about 60 teams, producing a generic content sample of 60,000 cases.
+In the fall of 2022, the subjects for this study were recruited to do the test.
+There were two interviews for this year's survey, and each research team bought a national sample of 1,000 people, which was conducted at YouGov in Redwood City, California.
+The paper will also analyze the sample of 1,000 people.
+CES used the data by taking samples and matching the data a second time.
+Finally, the survey results provide enough sample variables and the final data displayed, which can be re-entered into data cleaning and combined with other data to draw new conclusions.
+This paper is to select a few of the variables given and apply new filters and combinations to demonstrate whether the data generation is accurate.
 
-The remainder of this paper is structured as follows. @sec-data....
-
-We use the dataset from 2022 Cooperative Election Study @ces2022. To further enable the analysis I employed the use of the package of ggplot[@ggplot2] to generate histograms.
+We use R[@citeR] and the dataset from 2022 Cooperative Election Study @ces2022.
+To further enable the analysis I employed the use of the following packages: dataverse[@dataverse], ggplot[@ggplot2], tidyverse[@tidyverse], arrow[@arrow], rstanarm[@rstanarm], modelsummary[@modelsummary] and here[@here].
 
@@
 
-Talk more about it.
+## Data Source and variable
+The data we used came from The 2022 Cooperative Election Study (CES) and because the database was too large and conducted on the web, with a total of 60,000 people participating in the campaign, YouGov used a matching random sample survey and sample to match these adult U.S.
+citizens and categorized these groups as gender, race and age.
+We mainly use two variables, gender and education, to analyze as Biden and Trump vote rating.
 
-Talk way more about it.
+When we use dataset @dataverse data, the data shows that several variables about "votereg", "presvote20post", "gender" and "edu" represent the voter, the voting status for 20 years, the gender of the voter, and the education level of the voter.
+First of all, we will use @tidyverse for the simulate data part, and we get that there are 5 parts of the education level, from education level below high school to post-grad.
+At the same time, the data shows that there are four groups of genders, namely men, women, non-binary and other.
+In data cleaning, we're putting presidential candidates in the middle to show their respective approval ratings, and we're going to @tidyverse and @arrow Use "presvote0post" to filter, if "presvote0post" ==1, it will show Biden's approval rating, otherwise it will be Trump.
+This time, the data combines the voters' choice as well as their gender and education level, which are one of the factors.
+
+We know from the data that 4,000 more women voted than men.
+Compare with man, women voters are more likely to vote for Biden, regardless of their educational stage.
+Men generally have higher approval ratings for Biden than Trump, except for men at the high school graduate level.
+Non-binary support for Biden almost crushed trump's votes, with the smallest number of people in the other group, with half and half turnout for Biden and Trump.
+
+## Data methodology
+
+The 2022 United States Election Voter Survey is to select a representative sample within a sample group to conduct feedback and conduct in-depth surveys in order to ensure the generation of real data.
+In this way, when used for large-scale events such as elections in the United States, the fund of the web can greatly reduce the cost of expenses and the asymmetry of information generated by individuals.
+Digging deeper into the data, a matching method can be used for sample selectivity.
+The YouGov sample selection method is divided into two phases.
+First, they randomly selected a representative target sample from the target population.
+A matching sample is similar for the random sample and they will match it when the data can be matched.
+The matching process uses several variables to ensure that the matched sample is similar in measurement characteristics to the target sample.
+For example, gender will be divided into 4 different groups to vote within the group, in order to understand the choice by different genders people who chosen Biden.
+Further, we can combine the people of different genders with their educational backgrounds to analyze whether there are differences in the turnout rate of people in the same group due to different levels of education in different educational backgrounds.
+
+## Weighting
+The target sample does not fit the demographics perfectly, and any remaining imbalances in the sample need to be weighted.
+Therefore, after the CES weighted the sample, the politically charged citizens were balanced in the distribution of multiple voter turnouts such as gender and education.
+Weighting is performed for samples in two parts.
+First, the 2020 presidential ballot was weighted by iterative proportional fitting ("skew") of joint distribution, and different states were selected as representative samples, so that the full cases could be weighted into the sampling framework using entropy balance.
+Then voters and other conditions were in a state of equilibrium, and the content of common content was cut out to reduce the proportion of data.
+In the second phase, CES used a matching method to conduct new weighting in 2022, which will ensure the diversity of the sample and understand the voting choices of different voters.
+
+## Vote Validation
+In order to ensure that the data matches the TargetSmart, the lost of some data may not be matched.
+First, we download the file from dataverse @dataverse to get the raw data, then we assign the sample, record the missing data, and test it.
+"TS_voterstatus" represents whether the voter is active or not.
+Then to "TS_g2022" about the status of whether voters vote or not, in 2022, CES recorded about 49% of people voting in the primary choice and 81% voting in the general election.
+He showed that if any non-missing value is less than 7, then the election has a verified voting record, which is possible to be matched.
+We mainly use "CC22_401" to verify turnout, so that we can do the next step of matching and filter out data loss.
+If we want to verify the turnout of the CES, we can use three methods: variables and self-reported turnout - “TS_g2022" and whether it has been registered.
+To collect the primary election whether it is online or not, and then enter the system and survey and then determine whether they will participate in the general election for the second round, and how to participate in the selection method can also become a direction of analysis, because the data is too large, as mentioned above, it may be that the web will conduct the main voting method, but it is not excluded that other ways can also participate in the vote.
+Multivariate samples can lead to more data matching.
+Combined with the two main elements we used above about gender and education, we can end up with a complete and accurate output of data.
 
@@
 Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.
+$\alpha$ represents the intercept term, which is the log-odds of the outcome variable when all predictor variables are equal to zero.
 $\beta_1$ and $\beta_2$ represent the coefficients associated with the predictor variables (gender and education level of respondent, respectively).

### 2024-03-17 paper/datasheet.qmd
Edits

@@
 title: "Datasheet for 'A dataset'"
-subtitle: "My subtitle if needed"
-author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
+author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
+thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
+date: "March 11, 2024"
 abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."

### 2024-03-17 paper/paper.qmd
add some details

@@
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
-thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
+thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>. Datasheet is inside the 'paper' folder."
 date: "March 11, 2024"
@@
 The analysis reveals a consistent trend: regardless of gender or education level, the majority of voters cast their ballots for Biden over Trump (@bartels2008unequal).
-Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections (@ansolabehere1995goin).
+Recognizing this phenomenon, the paper aims to conduct a deeper exploration into why Biden garnered widespread support and its potential implications for future elections (@ansolabehere1995going).
 
@@
 
-Another crucial insight gleaned from global observations is the importance of candidate appeal and campaign strategies in influencing voter preferences (@ansolabehere1995goin).
+Another crucial insight gleaned from global observations is the importance of candidate appeal and campaign strategies in influencing voter preferences (@ansolabehere1995going).
 Effective communication strategies, including resonant messaging and clear articulation of policy proposals, play a pivotal role in swaying undecided voters and mobilizing support from diverse demographic groups (@holbrook1996do).
@@
 
-Despite its contributions, this paper has several limitations that warrant acknowledgment (@ansolabehere1995goin).
+Despite its contributions, this paper has several limitations that warrant acknowledgment (@ansolabehere1995going).
 Firstly, while the analysis identifies correlations between gender, education, and candidate preference, it may overlook other influential factors such as race, age, and geographic location (@campbell1954voter).
@@
 Moving forward, further research is needed to deepen our understanding of the factors driving voter behavior and electoral outcomes (@bartels2008unequal).
-Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences (@ansolabehere1995goin).
+Future studies should employ more diverse sampling methods and incorporate qualitative methodologies to capture the nuances of voter preferences (@ansolabehere1995going).
 Additionally, exploring the intersectionality of demographic variables and considering evolving societal trends will enhance the comprehensiveness of analyses (@campbell1954voter).
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-\newpage
-
 # References

### 2024-03-17 paper/datasheet.qmd

@@
 1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
-    -- The Cooperative Election Study made the dataset was created to analyze the number of U.S.
-adult citizens who vote in U.S.
-elections and whether their background affects the probability of voting.
-Select each state as a sample, and then select matches from the middle for further investigation.
-In this way, the data obtained by combining multiple variables will be more accurate.
+    - The dataset was created to enable analysis of Australian politicians.
+We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - The Cooperative Election Study build this dataset and it was made of 60 groups.
+    - TBD
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - The 2022 Cooperative Election Study was supported by the National Science Foundation Award # 2148907. 
+    - TBD
 4. *Any other comments?*
-    - The data given by CES is general, and new data needs to be combined to form a more accurate result.
+    - TBD
 
@@
 Please provide a description.*
-	- The CES 2022 data represents the electoral behavior of voters when they cast their ballots for candidates, with examples showing that voters' choice lines differ by gender and education.
+	- TBD
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- CES has 60,000 cases. It divided the samples of these cases themselves into different variables, which he then screened and cleaned.
+	- TBD
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- The dataset does not include all instances, the data is too large, so the CES calculation uses each state to collect data.
-Voter status is also restricted, for example, to choosing respondents only among adult U.S.
-citizens.
-Each state's calculations are better at collecting local data and matching it.
-A lot of voter data may be lost, the data will not be matched, so the instance will not be able to match other samples.
+	- TBD
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- Instance included voter information, political party, election status, equipment participating in the election. These are all variables derived from CES raw data.
+	- TBD
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- Yes. For example, in the CES gender's label, his label is gender4.
+	- TBD
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- CES only records the data and does not show the corresponding trend, it is easy to analyze a single variable and cannot be combined togethe
+	- TBD
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- CES does not give relationships between individual instances, they are more like separate categories and then show data, for example, gender4 in only gender differentiation without adding people and other variables.
+	- TBD
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- No.
+	- TBD
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- The data recorded by the respondents was lost and could not be matched to the data in the next part of the sample.
+	- TBD
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- CES data was collected from individuals on the web or through YouGov's 1000 data survey. The data is kept at the Harvard Dataverse, where it is accessible to all.
+	- TBD
 11.
@@
 If so, please provide a description.*
-	- CES did not have data that could be classified as confidential because it did not involve excessive privacy exposure, and he asked respondents more about their status at the time of the election.
+	- TBD
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- Data sets about gender issues and sexual orientation may offend respondents.
+	- TBD
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- There are a lot of sub-populations in the data.
-For example, based on gender, there will not be a single gender, but a variety of genders for respondents to choose from.
-Secondly, there are 5 education levels.
-In terms of age, most of the respondents were adults, so the lowest age was from 18 and then all the way up to 65 and over.
+	- TBD
 14.
@@
 If so, please describe how.*
-	- No, he did not specify a particular person, the data is more to gather each person's data into different categories.
+	- TBD
 15.
@@
 If so, please provide a description.*
-	- Dataset Indicates sensitive data. The Dataset covers race, ethnic origin, religious beliefs, political views, party affiliation, sexual orientation, health data, and crime.
+	- TBD
 16. *Any other comments?*
-	- No.
+	- TBD
 

### 2024-03-17 paper/paper.qmd

@@
 author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
-thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>. Datasheet is inside the 'paper' folder."
+thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
 date: "March 11, 2024"

### 2024-03-17 paper/datasheet.qmd
aa

--- 2024-03-17 paper/datasheet.qmd
@@
 If so, please describe how.*
-	- TBD
+	- They collect information from YouGov, which collects a random sample of 1,000 people, and from individual respondents, who collect information using reported data, for example, on the web.
+After an initial screening, the missing data will not be matched. Therefore, collection is carried out after matching corresponding samples to improve the accuracy of data.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- CES data is collected online through the web. Sample matching is used to balance the whole data.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- The CES dataset uses the web to collect large amounts of data and to enter secondary data updates with smaller samples.
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- CES has more than 60 teams conducting research with around 60,000 respondents, but does not show how many are paid.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- The first questionnaire was in the field from September 29 to November 8; the post-election wave was from November 10 to December 15.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	-  No,there is no ethical review processes in the text.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- CES data was collected from the web, and the website collected data from the respondents.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- Yes, the individuals was indicated on the website that the data was collected.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- Yes, the Respondent personally knows that their data will be collected and used, because the respondent's voter registration status mentions whether the respondent is active or not.
+And in each of the following options there is an absence or other state.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- There is no claim of a mechanism for withdrawing consent in the future or for certain purposes.
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- CES only provides data on a single variable and no more data analysis.
 12. *Any other comments?*
-	- TBD
+	- No
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Four will be selected first for distribution, followed by voteberg, educ, gender4 and the voters.
+And then it was cleaned it up a little bit, filter voteberg out of 1.
+We say votereg == 1, presvote20post %in% c(1, 2)) votereg equals 1 which means the respondent can vote.
+Filter out the ones that aren't votereg and aren't 1 or only look at people who register to vote.
+presvote20post %in% c(1,  2) Means 2020 President Vote Post Election Who did you vote for in the election for President in 2020 presvote20post.
+However, it only focus on Biden or Trump, so we are second.
+It only select these four columns presvote20post votebreg, educ and gender4 in the raw dataset for variable study.
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- CES Guide 2022 does not have any other raw data except for the data recorded on voter turnout
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- No
 4. *Any other comments?*
-	- TBD
+	- I think CES needs to create more data and put it out there.
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- CES does not give any tasks, it just provides data reference.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- CES does not give a repository of any papers or systems for the dataset, which is mostly obtained directly through the Web.
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- Data sets can be used to analyze the influence of gender, age, race and so on on politics.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- The composition of the data or other manipulation can affect the unfair treatment of individuals or groups, for example, if a group mostly supports Biden, it is likely that they will suffer discrimination from fans of Trump or other candidates.
+So we increase the balance by weighting, which allows for more accurate data with less bias.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- No, data sets can do a lot of things.
 6. *Any other comments?*
-	- TBD
+	- No
 
@@
 If so, please provide a description.*
-	- TBD
+	- CES data sets are sent to Harvard University's Dataverse, and the corresponding information is available.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- The dataset is available for study and study on the website in the form of doi:10.7910/DVN/PR4L8P.
 3. *When will the dataset be distributed?*
-	- TBD
+	- The author has released four Dataset versions.
+The Dataset version first existed on 2023-03-20, this one was followed by 2023-03-21 and 4-08, the authors added citation Metadata and Files2.
+The final version was voted validation by TsrgetSmart to increase the authenticity and accuracy of the data.
 4.
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- Zheng(Zeb) Yang
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- zhengzeb.yang@mail.utoronto.ca
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- Not yet.
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- Yes, we will update the dataset in a timely manner according to the requirements listed in the replies received in the mailbox from the dataset consumers. 
 5.

### 2024-03-17 paper/datasheet.qmd
renew the content

@@
 ---
-title: "Datasheet for 'A dataset'"
-subtitle: "My subtitle if needed"
+title: "Datasheet for 'US-Political-Support'"
+
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+  - Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun
+thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
+
 format: pdf
